---
title: "BS1811-1516 Financial Analytics Assignment 1"
author: "C.K. Poon, Jin Lee, Chan Baik, Yujia Ren, Siang Lau"
date: "30 May 2016"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    theme: spacelab
    number_sections: yes
---
```{r setup, include = FALSE}
# Set knitr options
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(readr)
library(dplyr)
library(tidyr)
library(knitr)
library(ggplot2)
```

# Introduction
To be written

# Data Preparation

**Step 1** - Load the data
```{r step_1}
#Reading data

```


# CVA pricing

## Part i
Write your own Black Scholes function and price [= CBS] a simple call option with the following
inputs:
```{r}

```

## Part ii
Implement a Geometric Brownian Motion (GBM) for the Equity underlying process
```{r}

```

## Part iii
Use your Black Scholes function and the paths derived in the previous step to
```{r}

```

## Part iv
Use the MtM distributions from the previous step [a matrix (13110000) is expected] and calcu-
late the Expected Exposure (EE), the Potential Future Exposure (PFE) at 95% condence level
and the CVA price using the following counterparty spread curve:
```{r}

```

## Part v
Now add a second option trade in the portfolio.
```{r}

```


# Option pricing
## Part 1
## Part 2
## Part 3


# Backtesting
## Part 1
```{r}

```

## Part 2
```{r}

```

## Part 3
```{r}

```


# Reference
* Reference 1
* Reference 2